%-------------------------------------
% LaTeX Template for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[letterpaper,11pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{tcolorbox}


%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Ethan Haque}
\def \subtitle {Full Stack Developer}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/ethan-haque}
\def \linkedintext {/Ethan-Haque}

\def \phoneicon {\faPhone}
\def \phonetext {250-880-4402}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:eth.haque@gmail.com}
\def \emailtext {Eth.Haque@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/Ethan-Haque}
\def \githubtext {/Ethan-Haque}

 \def \websiteicon {\faGlobe}
 \def \websitelink {https://ethanhaque.ca}
 \def \websitetext {EthanHaque.ca}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{191919}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{0D47A1}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \tcbox[on line,boxsep=0pt,left=2pt,right=2pt,top=2pt,bottom=2pt,colback=secondary]
  {\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} \\
          {\faHome} Victoria BC
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{}{\website}{\email}{\phone} % Set the order of items here


%-------------------------------------------------- WORK EXPERIENCE --------------------------------------------------
\section{\faPieChart}{Work Experience}

\resumeEntryStart
    \resumeEntryTSDL
      {E-Porter}{Aug 2022 - Present}
      {Full Stack Developer}{Full time}
    \resumeItemListStart
      \resumeItem {Drive the entirety of technology operations for E-Porter, overseeing the management and enhancement of the landing page, web app, mobile app, and backend.}
      \resumeItemListStart
        \resumeItem {Developed and maintained full-stack features across Angular, Node.js, MongoDB, Ionic, and Next.js.}
        \resumeItem{Built responsive, user-focused interfaces for both mobile and desktop platforms.}
        \resumeItem{Managed hosting infrastructure, backups, and App Store operations to guarantee uninterrupted functionality.}
        \resumeItem{Worked closely with stakeholders to align features with business needs.}
      \resumeItemListEnd
      \resumeItem {Angular, TypeScript, Node.js, MongoDB, CSS, Express, Ionic, Docker, Google API, Mapbox, Stripe, Next.js, React}
    \resumeItemListEnd

    \resumeEntryTSDL
      {Three Trees Technical | Consulting for E-Porter}{Nov 2021 -- Jun 2022}
      {Full Stack Developer}{Full time}
    \resumeItemListStart
      \resumeItem {Developed an end-to-end package delivery system in collaboration with a small team for E-Porter.}
      \resumeItemListStart
        \resumeItem {Designed and implemented web and mobile app pages, ensuring a responsive design for optimal user experiences.} 
        \resumeItem {Engineered database models, API controllers, and routing systems for seamless integration of payment processing, delivery operations, user management, and related entities.}
      \resumeItemListEnd
      \resumeItem {Angular, TypeScript, Node.js, MongoDB, CSS, Express, Ionic, Docker, Google API, MapBox, Firebase, BitBucket.}
    \resumeItemListEnd

    \resumeEntryTSDL
      {Metl Solutions}{May 2021 - Aug 2021}
      {Backend Developer}{Internship}
    \resumeItemListStart
      \resumeItem {Worked with a team of Capstone students to develop and integrate an MS Teams bot leveraging their API.}
      \resumeItemListStart
          \resumeItem {Specialized in chat event handling and backend implementation for the bot.}
          \resumeItem {Adapted and optimized API REST functions for seamless MS Teams integration.}
       \resumeItemListEnd
       \resumeItem {Node.js, Python, and Django.}
    \resumeItemListEnd
  \resumeEntryEnd

%---------------------------------------------- Client Websites ----------------------------------------------
\section{\faDesktop}{Client Websites}

\resumeEntryStart
    \resumeEntryTD
      {E-Porter}{\href{https://eporter.com/}{eporter.com}}
    \resumeItemListStart
    \resumeItem{Rebuilt a slow WordPress site into a high-performance Next.js application, critical for drivers needing reliable access in low-connectivity areas.}
    \resumeItemListStart
          \resumeItem {Reduced load times from over 12 seconds to under 1 second, greatly improving speed and usability.}
          \resumeItem {Improved SEO and responsiveness for better search visibility and a seamless experience across devices.}
       \resumeItemListEnd
       \resumeItem {Next.js, React, TailwindCSS}
    \resumeItemListEnd

  \resumeEntryTD
      {Platinum Consulting \& Co.}{\href{https://platinumconsultingco.com/}{platinumconsultingco.com}}
    \resumeItemListStart
    \resumeItem{Developed a modern, brand-aligned business website with a focus on search visibility and user experience.}
    \resumeItemListStart
          \resumeItem {Leveraged Astro’s static-site generation for near-instant page loads and top-tier Lighthouse scores.}
          \resumeItem {Integrated dynamic React components for interactive features without sacrificing performance.}
       \resumeItemListEnd
       \resumeItem {Astro, React, TailwindCSS}
    \resumeItemListEnd
  \resumeEntryEnd

%-------------------------------------------------- EDUCATION --------------------------------------------------
\section{\faGraduationCap}{Education}
  \resumeEntryStart
    \resumeEntryTSDL
      {Camosun College}{Sept 2019 - Aug 2021}
      {Information and Computer Systems}{Diploma}
      \resumeItemListStart
      \resumeItem {Acquired practical skills in programming, software deployment, security, and maintenance to meet industry standards.}
      \resumeItem{Gained hands-on experience in web and mobile programming, database design and management, software design, and the operations and maintenance of networks and software.}
      \resumeItemListEnd
  \resumeEntryEnd
  
%-------------------------------------------------- PROGRAMMING SKILLS --------------------------------------------------
\section{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Languages} {HTML, JavaScript, TypeScript, CSS, SQL, Java, Python, C++, C\#, Swift, PHP}
  \resumeEntryS{Frameworks \& Databases} {Node.js, Angular, React, Next.js , MongoDB, Django, PostgreSQL, MySQL, Ionic}
  \resumeEntryS{Tools \& Services} {Docker, Git, GitHub, BitBucket, SourceTree, XCode, AWS, Google CP \& API, Mapbox, Stripe, Firebase, Linux}
 \resumeEntryEnd

\end{document}